---
title: "Using shinyLikert in a UI/Server setup"
author: "Gregor de Cillia"
output: html_document
runtime: shiny
---

The `shinyLikert` package is meant to be used in interactive sessions. There are basically tow ways to run interactive content: shinyMarkdown files and standalone apps using a ui/server setup. These examples will show you how to use the latter.

## In the R terminal

To use the package in the console, you can use the command `shinyApp` for interactivity. For example, you can copy/paste the following in your console.

```{r, message=FALSE}
library(shinyLikert)
```

```{r, ref.label="renderFactorOverview", eval=FALSE}
```

Now a new window will open showing the following output.

```{r renderFactorOverview, echo=FALSE}
 shinyApp(
       ui= fluidPage(
         uiOutput( "selector" ),
         uiOutput( "plot" )
       ),
       server = function(input,output,session){
         testData3 = createTestData( participants = 100,
                                     questions    = 10   )
         rendered = renderFactorOverview(
           testData3
           )
         output$plot     = renderUI({rendered$plot})
         output$selector = renderUI({rendered$selector})
       }
     )
```

Note that the `output` object is used to transfer the plot and selector from the server to the ui.

## With ui.R and server.R as seperate scripts

Alternatively, you can create two files `ui.R` and `server.R` containing the `ui` and `server` arguments wrapped by `shinyUI` and `shinyServer`. Then place them in the same folder. Here is the content of `ui.R`

```{r, eval=FALSE}
library(shinyLikert)
shinyUI( 
  fluidPage(
    uiOutput( "selector" ),
    uiOutput( "plot" )
  )
)
```

the `server.R` file should look as follows

```{r, eval=FALSE}
library(shinyLikert)
shinyServer(
  function(input, output) {
    testData3 = createTestData( participants = 100,
                                questions    = 10   )
    rendered = renderFactorOverview(
      testData3
    )
    output$plot     = renderUI({rendered$plot})
    output$selector = renderUI({rendered$selector})
  }
)  

```

Now you can run the app using

```{r, eval=FALSE}
runApp( "path/to/folder/containing/ui.R/and/server.R" )
```

The path can be either global or local to your working directory (see `?getwd` for help). The defailt argument of `runApp` is our current working directory. This means, you can run the app with

```{r, eval=FALSE}
runApp()
```

in case your working directory is the one containing the `ui.R` and `server.R` files.

## Compability with RMarkdown files

copying the above `shinyApp` command into a chunk of a ShinyMarkdown also works. The app then appears inside the document.

##Another example

Here is another example of a ui/server setup.

```{r}
shinyApp(
    ui= fluidPage(
        uiOutput( "rendered" )
      ),
    server = function(input,output,session){
      testData3 = createTestData( participants = 100, 
                                  questions    = 10   )
      rendered = renderShinyLikert( 
        testData3 ,
        dropdown = "gender" )

      output$rendered = renderUI( plot( rendered ) )
    },
    options = list(height = 600)
  )
```

